Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Not here
Reformulation is in the conclusion
We used the CP codes

\section{Introduction}
\todo{talk about subgraph isomorphism applications, particularly vision}
\todo{talk about reformulating}
The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
\emph{target} graph. It comes in two forms: in the non-induced variant, edges must be mapped to
edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges may only be
mapped to non-edges. When a pattern cannot be found, we may wish to be given a result which maps as
many vertices of the pattern into the target as possible. In the induced case, this is known as the
maximum common induced subgraph problem (we discuss the non-induced case below). However, although
recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
vertices, the state of the art for the maximum common subgraph problem becomes computationally
infeasible at only 35 vertices when working with unlabelled graphs
\citep{DBLP:conf/cp/McCreeshNPS16}. This is largely because strong inference, based upon the degrees
of vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
but not maximum common subgraph, and so the state space in the former is much more restricted,
whilst filtering during search is vastly stronger.

@@

?? Explain effectively-unit domain, multiple $\bot$ values.

@@

We perform our experiments on systems with dual Intel Xeon CPU E5-2640 processors with 64GBytes of
RAM, running Ubuntu 14.04. Our algorithm was implemented in C++\footnote{URL removed for anonymous
review}, and source code was compiled using
GCC 5.3.0. We used a timeout of 1,000 seconds for each instance.

For datasets, we use the same 5,725 instances used in a recent work on portfolios of algorithms for
subgraph isomorphism \cite{thelionpaper}. This collection includes randomly generated scale-free
graphs \cite{constraints10}, an assortment of real-world graphs of varying sizes \cite{LV02},
randomly generated graph pairs (using bounded degree, regular mesh, and uniform models; all are
satisfiable), segmented images~\cite{pr15,cviu11}, meshes from modelling 3D objects \cite{cviu11},
and graphs close to the satisfiable-unsatisfiable phase transition
\cite{DBLP:conf/ijcai/McCreeshPT16}; all these instances are available in a simple text
format\footnote{\texttt{http://liris.cnrs.fr/csolnon/SIP.html}}.

?? Using the French code, and the Glasgow clique code.

Note that many of these instances are \emph{much} larger than were used in the recent comparison of
maximum common subgraph algorithms by \citet{DBLP:conf/cp/McCreeshNPS16}: for unlabelled graphs,
they used pairs of graphs with up to 35 vertices in each, whilst our dataset contains patterns with
up to ?? vertices and targets with up to ?? vertices. For maximum common subgraph, 1,560 of the
instances cannot fit in the amount of RAM we have available---we treat these instances as having
timed out. The situation for the clique encoding is even worse, and 3,653 of these instances do not
fit in RAM. In contrast, for our algorithm, every instance fits comfortably (at least on modern
server-class hardware).

>>>>

\section{Introduction}
\todo{talk about subgraph isomorphism applications, particularly vision}

The subgraph isomorphism problem is to find a copy of a small \emph{pattern} graph inside a larger
\emph{target} graph. It comes in two forms: in the non-induced variant, edges must be mapped to
edges, but the target may have ``extra edges'', whilst in the induced variant, non-edges may only be
mapped to non-edges. When a pattern cannot be found, we may wish to be given a result which maps as
many vertices of the pattern into the target as possible. In the induced case, this is known as the
maximum common induced subgraph problem (we discuss the non-induced case below). However, although
recent subgraph isomorphism algorithms are comfortable working with graphs with thousands of
vertices, the state of the art for the maximum common subgraph problem becomes computationally
infeasible at only 35 vertices when working with unlabelled graphs
\citep{DBLP:conf/cp/McCreeshNPS16}. This is largely because strong inference, based upon the degrees
of vertices \citep{DBLP:journals/ai/Solnon10} and the distances or paths between them
\citep{DBLP:conf/cp/AudemardLMGP14,DBLP:conf/cp/McCreeshP15}, is possible with subgraph isomorphism,
but not maximum common subgraph, and so the state space in the former is much more restricted,
whilst filtering during search is vastly stronger.

@@

@@

We perform our experiments on systems with dual Intel Xeon CPU E5-2640 processors with 64GBytes of
RAM, running Ubuntu 14.04. Our algorithm was implemented in C++\footnote{URL removed for anonymous
review}, and source code was compiled using
GCC 5.3.0. We used a timeout of 1,000 seconds for each instance. For comparison, we used the
implementations of \citet{DBLP:conf/cp/McCreeshNPS16}.

For datasets, we use the same 5,725 instances used in a recent work on portfolios of algorithms for
subgraph isomorphism \cite{thelionpaper}. This collection includes randomly generated scale-free
graphs \cite{constraints10}, an assortment of real-world graphs of varying sizes \cite{LV02},
randomly generated graph pairs (using bounded degree, regular mesh, and uniform models; all are
satisfiable), segmented images~\cite{pr15,cviu11}, meshes from modelling 3D objects \cite{cviu11},
and graphs close to the satisfiable-unsatisfiable phase transition
\cite{DBLP:conf/ijcai/McCreeshPT16}; all these instances are available in a simple text
format\footnote{\texttt{http://liris.cnrs.fr/csolnon/SIP.html}}.
Note that many of these instances are \emph{much} larger than were used in the recent comparison of
maximum common subgraph algorithms by \citet{DBLP:conf/cp/McCreeshNPS16}: for unlabelled graphs,
they used pairs of graphs with up to 35 vertices in each, whilst our dataset contains patterns with
up to ?? vertices and targets with up to ?? vertices. For maximum common subgraph, 1,560 of the
instances cannot fit in the amount of RAM we have available---we treat these instances as having
timed out. The situation for the clique encoding is even worse, and 3,653 of these instances do not
fit in RAM. In contrast, for our algorithm, every instance fits comfortably (at least on modern
server-class hardware).
